\documentclass[margin]{res}
% \usepackage{utopia}
\usepackage{graphics}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc} % This package will support Turkish chars
\renewcommand{\sectionfont}{\bfseries\scshape}
\renewcommand{\sectionskip}{0.2 in}
\setlength{\textwidth}{5.2in}
\setlength{\textheight}{650pt}

% \addtolength{\lmargin}{-5in}
% \usepackage{geometry}
% \geometry{
%      a4paper,
%     %  total={170mm,257mm},
%     %  left=20mm,
%     %  top=20mm,
% }

% \usepackage[legalpaper, portrait, margin=1in]{geometry}

\begin{document}
\begin{resume}
\vspace{-5em}
\moveleft.5\hoffset\centerline{\bfseries{\Large{Baraa Orabi}} (he/him/his)} 
\smallskip

\moveleft.5\hoffset\centerline{
	+1 778-751-4364
	\quad \textbullet \quad
	\href{mailto:baraaorabi@gmail.com}{baraaorabi@gmail.com}
	\quad \textbullet \quad 
	\href{https://www.github.com/baraaorabi}{GitHub: baraaorabi}
	\quad \textbullet \quad 
	\href{https://www.linkedin.com/in/baraaorabi}{LinkedIn: baraaorabi}
}
% \moveleft.5\hoffset\centerline{
%     202-1125 10th W Ave, Vancouver, BC, Canada V6H 1J2
% }

\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}

	\section{Education}
    	\textbf{Ph.D. in Computer Science}  \hfill \textit{Sep 2019 - Aug 2024} \\
    	\href{https://cs.ubc.ca/}{\textit{University of British Columbia}},
    	Supervisors: Drs. \href{http://hachlab.org/}{Faraz Hach} and \href{https://cchauve.github.io/}{Cedric Chauve}\\
    % 	\textit{Vancouver, BC}\\
    % 	Cumulative GPA of 4.20/4.00\\
    % 	Supervised by \href{http://hachlab.org/}{Prof. Faraz Hach} and \href{http://www.cecm.sfu.ca/~cchauve/}{Prof. Cedric Chauve}\\
    	\vspace{-1em}
        \begin{itemize}[leftmargin=*]
    	    \item Develops novel algorithms and data structures for high throughput genomic and transcriptomic sequencing that focus on minimizing dependence on references.
    	   % \item Supervisors:  Profs \href{http://hachlab.org/}{Faraz Hach} and \href{https://cchauve.github.io/}{Cedric Chauve}.
    	\end{itemize}

    	\textbf{M.Sc. in Computing Science}  \hfill \textit{Sep 2017 - Dec 2018} \\
    	\href{http://www.sfu.ca/computing.html}{\textit{Simon Fraser University}},
    	Supervisors: Drs. \href{http://hachlab.org/}{Faraz Hach} and \href{https://cchauve.github.io/}{Cedric Chauve}\\
    	\vspace{-1em}
        \begin{itemize}[leftmargin=*]
    	    \item Thesis: Alignment-free clustering and error correction of UMI tagged DNA molecules
    	   % \item Supervisors:  Profs \href{http://hachlab.org/}{Faraz Hach} and \href{https://cchauve.github.io/}{Cedric Chauve}.
    	\end{itemize}
    	
    
    	\textbf{B.Sc. in Computer Engineering}  \hfill \textit{Jan 2013 - Aug 2017} \\
    	\href{http://cs.bilkent.edu.tr/}{\textit{Bilkent University}},
    	Supervisor: \href{http://www.cs.bilkent.edu.tr/~calkan/}{Dr. Can Alkan}\\
    % 	\textit{Ankara, Turkey}\\
    	\vspace{-1em}
        \begin{itemize}[leftmargin=*]
    	    \item Worked on structural variation discovery using combinatorial analysis of 10x Genomics Linked-reads
    	\end{itemize}

    %     \textbf{Minor in Philosophy}  \hfill \textit{Sep 2014 - Sep 2016 (Terminated)} \\
    % 	\href{http://www.phil.bilkent.edu.tr/}{Bilkent University}\\ \textit{Ankara, Turkey}\\
    % % 	Cumulative GPA of 3.80/4.00\\
    % 	I focused on analytical philosophy including philosophy of science and mind.
    	
    % 	\textbf{High School Diploma}  \hfill \textit{Sep 2006 - May 2012} \\
    % 	\href{http://fikr.edu.sa/}{Dar Al Fikr Boys Schools}\\ \textit{Jeddah, Saudi Arabia}\\
    %     Cumulative GPA of 4.00/4.00\\
    %     Awarded full scholarship for 6 years

	\section{Research Experience}
        \textbf{Research Assistant, \href{http://www.prostatecentre.com/about-us/people/dr-faraz-hach}{{Vancouver Prostate Centre}}}  \hfill \textit{Sep 2017 - present} \\
    	\vspace{-1em}
        \begin{itemize}[leftmargin=*]
    	   % \item Designs solutions for the computational problems of high throughput cancer genomic and transcriptomic sequencing.
    	    \item Develops scalable and efficient algorithms for clustering, error-correction, with focus on linked-reads and long-reads technologies.
    	    \item Managerial responsibilities including organizing data storage, publishing software packages, and running the lab's social media presence
    	\end{itemize}

    	\textbf{Research Intern, \href{http://www.genomize.com}{Genomize Inc.}}  \hfill \textit{June 2017 - Aug 2017} \\
    	\vspace{-1em}
        \begin{itemize}[leftmargin=*]
    	    \item Worked on integrating different genomic variant callers for use by \href{https://seq.genomize.com}{SEQ}, an easy-to-use, genome-based medical diagnostic tool.
    	\end{itemize}
    % 	I worked My work was supervised by Drs. \href{https://www.linkedin.com/in/ersen-kavak-phd-a5109953/}{Erşen Kavak} and \href{https://www.linkedin.com/in/guzin-tunca-5a001848/}{Güzin Tunca}.

        \textbf{Research Volunteer, \href{http://alkanlab.org/}{Bilkent University}}  \hfill \textit{Jan 2016 - Aug 2017} \\
    	\vspace{-1em}
        \begin{itemize}[leftmargin=*]
    	    \item Worked on genomic structural variation discovery using combinatorial analysis of 10x Genomics Linked-reads. 
    	\end{itemize}
    % 	I My work was supervised by \href{www.cs.bilkent.edu.tr/~calkan/}{Prof. Can Alkan} of Bilkent University and \href{http://www.imanh.org/}{Prof. Iman Hajirasouliha} of Weill Cornell Medical College.

% \vspace{4em}
	\section{Work Experience}
    	\textbf{Academic and Teaching Assistant, UBC}  \hfill \textit{Sep 2019 - Dec 2020} \\
    % 	\href{https://www.cs.ubc.ca/}{\textit{University of British Columbia}}\\
    	\vspace{-1em}
        \begin{itemize}[leftmargin=*]
            \item \textbf{Fall 2020 CPSC221 Basic Algorithms and Data Structures}: Ran three lab sections. Taught and communicated fundamental computer science concepts to 80+ students new to program.
            \item \textbf{Spring 2020 CPSC445 Bioinformatics Algorithms}: Co-designed course curriculum and developed original lecture notes (500+ slides).
            \item \textbf{Fall 2019 CPSC430 Computers and Society}: Held office hours (2 hours/week) and graded 600+ essays by over 100 students.
        \end{itemize}
    	
    	\textbf{Software Engineering Intern, Google}  \hfill \textit{Jun 2016 - Aug 2016} \\
    % 	\href{http://google.com/}{\textit{Google Inc.}}\\
    	\vspace{-1em}
        \begin{itemize}[leftmargin=*]
    	    \item Implemented a stage of migrating existing Remote Procedure Calls (RPCs) to in-server process calls, including writing A/B tests, on Google Display Ads Network front-end infrastructure
            % \item Learned new systems and languages, including Protocol Buffers, Google Borg deployment and testing system, and new C++ memory management features.
    	\end{itemize}   
    	
    \section{Publications}
    
\begin{enumerate}[leftmargin=*]
    \item Karaoglanoglu F, \textbf{Orabi B}, Chauve C, Hach F. 
    \textit{TKSM: Highly modular, user-customizable, and scalable transcriptomic sequencing long-read simulator.}
    bioRxiv. 2023.  
    \href{https://doi.org/10.1101/2023.06.12.544410}{doi:10.1101/2023.06.12.544410}. \textbf{Under review at OUP Bioinformatics}
    \item \textbf{Orabi B}, Xie N, McConeghy B, Xuesen D, Chauve C, Hach F. 
    \textit{Freddie: Annotation-independent detection and discovery of transcriptomic alternative splicing isoforms using long-read sequencing.}
    Nucleic Acids Research. 2023.  
    \href{https://doi.org/10.1093/nar/gkac1112}{doi:10.1093/nar/gkac1112}. \textbf{Accepted to RECOMB 2021}
    \item Ebrahimi G, \textbf{Orabi B}, Robinson M, Chauve C, Flannigan R, Hach F.
    \textit{Fast and accurate matching of cellular barcodes across short-reads and long-reads of single-cell RNA-seq experiments.}
    iScience. 2022.  
    \href{https://doi.org/10.1016/j.isci.2022.104530}{doi:10.1016/j.isci.2022.104530}. \textbf{Accepted to RECOMB-seq 2022}
    \item \textbf{Orabi B}, Erhan E, McConeghy B, Volik SV, LeBihan S, Bell R, Collins CC, Chauve C and Hach F. 
    \textit{Alignment-free Clustering of UMI Tagged DNA Molecules.} 
    Bioinformatics. 2018.
    \href{https://doi.org/10.1093/bioinformatics/bty888}{doi:10.1093/bioinformatics/bty888}. \textbf{Accepted to RECOMB-seq 2018} 

\end{enumerate}



    \section{Presentations}
	\textbf{\textit{Challenges of Isoform Identification and Discovery Using Long-read Sequencing}} \\
    \vspace{-1em}
    \begin{itemize}[leftmargin=*]
        \item Terry Fox Seminar Series, podium talk  \hfill \textit{Oct 2022}
	\end{itemize}

	\textbf{\textit{Freddie: Annotation-independent Detection and Discovery of Transcriptomic Alternative Splicing Isoforms}} \\
    \vspace{-1em}
    \begin{itemize}[leftmargin=*]
	    \item \href{https://www.recomb2021.org/accepted-papers}{RECOMB 2021}, podium talk   \hfill \textit{Sep 2021}
	    \item \href{https://www.iscb.org/cms_addon/conferences/ismb2020/tracks/rnacosi}{ISMB iRNA 2020}, short talk  \hfill \textit{July 2020}
	    \item {Lorne D. Sullivan Lectureship and Research Day}, short talk  \hfill \textit{July 2020}
        \item \href{http://www.vanbug.org/2020/raymond-ng/}{VanBUG}, student talk  \hfill \textit{Jan 2020}
        \item Terry Fox Seminar Series, podium talk  \hfill \textit{Oct 2019}
	\end{itemize}


	\textbf{\textit{Alignment-free Clustering of UMI Tagged DNA Molecules}} \\
    \vspace{-1em}
    \begin{itemize}[leftmargin=*]
	    \item \href{https://sites.google.com/site/sfuomics/omics-research-day/research2020}{SFU OMICS Research Day}, short talk  \hfill \textit{Jan 2019}
	    \item \href{https://web.archive.org/web/20180709093254/http://recomb2018.fr/recomb-seq}{RECOMB-seq 2018}, podium presentation  \hfill \textit{Oct 2018}
        \item \href{https://www.bigresearchday.com/}{BIG Research Day}, podium presentation  \hfill \textit{Mar 2018}
        \item \href{http://www.vanbug.org/}{VanBUG}, lightning talk  \hfill \textit{Dec 2017}
	\end{itemize}
    	
\section{Science communication and service}
    	\textbf{Finance VP, Graduate Student Association}    \hfill \textit{May 2021 - present} \\
	    \textit{\href{https://www.cs.ubc.ca/}{\textit{UBC}} Department of Computer Science }\\
    \vspace{-1em}
    \begin{itemize}[leftmargin=*]
	    \item Responsible for maintaining the accounting of annual budget and dispersing reimbursements for the graduate student body.
	\end{itemize}
 
    	\textbf{Member, faculty recruiting committee}    \hfill \textit{Sep 2020 - April 2021} \\
	    \textit{\href{https://www.cs.ubc.ca/}{\textit{UBC}} Department of Computer Science new tenure-track faculty recruiting committee}\\
    \vspace{-1em}
    \begin{itemize}[leftmargin=*]
	    \item Reviewed 60+ applications, interviewed 8 candidates, and organized candidate meetups with with graduate students in the department for the finalist candidates.
	\end{itemize}
    	
    	
% \vspace{3em}

    	\textbf{Organizer}, \textit{\href{http://www.vanbug.org/}{VanBUG}}  \hfill \textit{May 2018 - Aug 2023} \\
    	\textit{Monthly seminar and social event for the Vancouver bioinformatics community} \\ 
    \vspace{-1em}
    \begin{itemize}[leftmargin=*]
	   % \item 
	    \item Hosts the feature and students speakers, manages the website, and recruits student speakers.
	\end{itemize}
        

    	\textbf{Organizer}, \href{https://www.hackseq.com}{\textit{hackseq}}\hfill \textit{Mar 2018 - Dec 2020} \\
    	\textit{Annual Vancouver-based genomics hackathon turning ideas into open source software}\\
    \vspace{-1em}
    \begin{itemize}[leftmargin=*]
    	\item Recruited project leads, managed logistics, and hosted hackseq18 and hackseq19.
	\end{itemize}
    	

% \vspace{7em}
    	\textbf{Writer}, \href{http://qafilah.com/ar/writers/\%D8\%A7\%D9\%84\%D8\%A8\%D8\%B1\%D8\%A7\%D8\%A1-\%D8\%B9\%D8\%B1\%D8\%A7\%D8\%A8\%D9\%8A/}{\textit{Al Qafila Magazine}}  \hfill \textit{Mar 2014 - Apr 2017} \\
    	\textit{Al Qafila is a bi-monthly Arabic pop science magazine}\\
    \vspace{-1em}
    \begin{itemize}[leftmargin=*]
	    \item Wrote four articles on topics of computer science, philosophy of science, and open source movement.
	\end{itemize}
    	
        
    	
    	\textbf{Co-founder and presenter}, \href{https://soundcloud.com/a9far/}{\textit{A9far podcast}}  \hfill \textit{Jun 2013 - Sep 2014} \\
    % 	\\ 
    	\textit{A9far was an Arabic podcast discussing scientific topics}\\ 
    \vspace{-1em}
    \begin{itemize}[leftmargin=*]
	    \item Researched material, produced scripts, and co-presenting episodes totally over 20 hours of content.
	\end{itemize}
    	
    	
    	 

    	
%     \section{Awards and Honours}
% 	\textbf{SFU Applied Sciences Graduate Fellowship}  \hfill \textit{May 2018 - Aug 2018} \\
% 	\$3250 CAD awarded at the end of the 2018 summer semester.

% 	\textbf{NSERC-CREATE via BC Cancer Agency}  \hfill \textit{Sep 2017 - Aug 2018} \\
% 	\$22000 CAD over for the first year of masters program.

% 	\textbf{SFU Computing Science Graduate Fellowship}  \hfill \textit{Sep 2017 - Dec 2017} \\
% 	\$6700 CAD awarded at the start of the 2017 fall semester.

% 	\textbf{Bilkent Scholarships for International Students}  \hfill \textit{Sep 2012 - Aug 2017} \\
% 	80\% tuition waiver equalling to \$11600 USD per year. Awarded upon admission.

% 	\textbf{Bilkent Merit Based Scholarship}  \hfill \textit{Sep 2014 - Jun 2015} \\
% 	Full tuition waiver equalling \$14000 USD for one year. Awarded for ranking in the 1st percentile.

% 	\textbf{Dar Al Fikr High School Scholarship}  \hfill \textit{Sep 2006 - Jun 2012} \\
% 	Full tuition waiver equalling to \$11000 USD per year. Awarded upon admission.

% 	\textbf{Bilkent University High Honours}  \\
% 	Total of 6 semesters. Awarded for receiving greater than 3.50 GPA in the semester

% 	\textbf{Bilkent University Honours}   \\
% 	Total of 2 semesters. Awarded for receiving greater than 3.00 GPA in the semester

    

\section{Skills}
\begin{itemize}[leftmargin=*]
	\item \textbf{Programming Languages:} C/C++, Python, Unix systems, and Snakemake
	\item \textbf{Human Languages:} Arabic (native), English (fluent), Turkish (basic), Portuguese (basic)
	\item \textbf{Others:} Public speaking and communication, academic writing, teamwork
\end{itemize}
	
%     \section{Interests}
% 	\textbf{Computation}: Open source software, reproducible workflows, and hackathons
	
% 	\textbf{Other}: Public speaking and communication, analytic philosophy, linguistics, history, and politics

% 	


\end{resume}

\end{document}
